All Your Graphs Belong to Us

### 2012-07-17 doc/asplos13/implementation.tex
Fixed up broken imeplemention.tex and Makefile from last commit

Most study of work stealing assumes that a processor has one worker
thread and so it only steals when utilization would go to zero. 
%that is,when there are no more local tasks available. 
Grappa, on the other hand, relies on having many worker threads per core. The
core would be fully-utilized if there is always something on the ready
queue. Even if there are many active tasks, if they are all suspended
for long-latency network requests, then the core is underutilized.
So, there is a choice: should the core use some of this idle time to
do perform work stealing or should it just wait that local tasks will
create more work. We choose to have a core inititiate a steal when all
of the following conditions hold: no workers are ready to run, 
%\checkme{there are idle worker threads --not required to mention since
%technically would happen if have right number}
the unstarted task queues are empty, and there are no outstanding steal requests. 
Having one outstanding steal request allowed throttles steals to
prevent flooding the network, but other scalable quieting mechanisms
would be possible, such as voting tree\cite{scalable work stealing or
cilk98} or lifelines \cite{lifelines}. Termination detection is not
built into the Grappa task scheduler, rather, it is considered a programming error for
the program to exit without syncing all tasks.

\todo{where to put the following related}
Fork join computations: implement with futures or continuation passing
style
feed-forward computations: implement with scalable task counting (we
focus on this style in our benchmarks)
(breifly describe global task joiner)

>>>>

Most study of work stealing assumes that a processor has one worker
thread and so it only steals when utilization would go to zero. 
%that is,when there are no more local tasks available. 
Grappa, on the other hand, relies on having many worker threads per core. The
core would be fully-utilized if there is always something on the ready
queue. Even if there are many active tasks, if they are all suspended
for long-latency network requests, then the core is underutilized.
So, there is a choice: should the core use some of this idle time to
do perform work stealing or should it just wait that local tasks will
create more work. We choose to have a core inititiate a steal when all
of the following conditions hold: no workers are ready to run, 
%\checkme{there are idle worker threads --not required to mention since
%technically would happen if have right number}
the unstarted task queues are empty, and there are no outstanding steal requests. 
Having one outstanding steal request allowed throttles steals to
prevent flooding the network, but other scalable quieting mechanisms
would be possible, such as voting tree\cite{scalableWorkStealingOrCilk98}
or lifelines \cite{lifelines}. Termination detection is not
built into the Grappa task scheduler, rather, it is considered a programming error for
the program to exit without syncing all tasks.

\TODO{where to put the following related}
Fork join computations: implement with futures or continuation passing
style
feed-forward computations: implement with scalable task counting (we
focus on this style in our benchmarks)
(breifly describe global task joiner)
